\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sanjay Mohan Kumar} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{(571)307-0134 \\ \href{mailto:smohanku@gmu.edu}{smohanku@gmu.edu} \\ \href{https://linkedin.com/in/smohanku}{linkedin.com/in/smohanku} \\ \href{https://github.com/San68bot}{github.com/San68bot}}


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-0.5em}
\begin{rSection}{Education}

{\bf George Mason University} \hfill {Fairfax, VA}\\
Bachelor of Science in Computer Science \hfill{Aug 2022 - Dec 2024}\\
Masters of Science in Computer Science (Accelerated Masters program) \hfill{May 2024 - Dec 2025}\\
Coursework: Artificial Intelligence, Data Structures, Algorithms, Agile Software Engineering\\
Deans List: 2022 - 2024
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}
\textbf{Undergraduate Teaching Assistant} \hfill Aug 2023 - May 2024
 \begin{itemize}
    \itemsep -3pt {}
     \item Assisted Professors and GTAs in teaching Low-Level \& Computer Systems programming, supporting over 400 students each semester and contributing to an increase in class participation and engagement.
     \item Conducted mid-semester and end-of-semester review sessions, helping students improve their grades and fostering a collaborative learning environment.
 \end{itemize}
\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Self-Motivated PROJECTS}
\vspace{-0.75em}
\item{\textbf{Naviguide AI}}: \textit{Computer Vision $\vert$ AI} \vspace{0.5em}\\
\begin{itemize}
\vspace{-2em}
\itemsep -3pt
\item[--] Developed an AI for dynamic object detection and tracking, created autonomously calibrating vision parameters to minimize background noise and enhance environment.
\item[--] Designed a Neural Network for real-time user haptic feedback, enabling visually impaired individuals to perceive the direction and distance of nearby objects; ensured privacy by processing all data locally.
\item[--] Won 1\(^{st}\) place in the ``Best use of Artificial Intelligence'' track at PatriotHacks 2023 - 2024 Hackathon
\end{itemize}

\item{\textbf{AsyncFSM}}: \textit{Data Structures $\vert$ Algorithms} \vspace{0.5em} \\
\begin{itemize}
\vspace{-2em}
\itemsep -3pt
\item[--] Designed and developed a robust data structure, enabling non-blocking management and concurrent processing without risk of data corruption, spontaneously acts as data structure while allowing state machine operations
\item[--] Achieved \textit{O(1)} time complexity for data addition and \textit{O(n)} for searches and executions
\item[--] Ideal for multi-process applications desiring minimal latency and maximum efficiency.
\end{itemize}

\item{\textbf{VIMU Process Monitor}}: \textit{C $\vert$ Linux/Unix} \vspace{0.5em} \\
\begin{itemize}
\vspace{-2em}
\itemsep -3pt
\item[--] Developed the VIMU monitor using C, featuring an interactive command-line shell for executing, inspecting, and managing multiple tasks, with support for file redirection and inter-process communication.
\item[--] Implemented efficient logging, signal handling, and error reporting functions to ensure consistent output and successful concurrent process management in a Unix operating system.
\end{itemize}

\item{\textbf{BlockIdentity}}: \textit{Blockchain $\vert$ Data Structures $\vert$ Smart Contracts} \vspace{0.5em}\\
\begin{itemize}
\vspace{-2em}
\itemsep -3pt
\item[--] Developed a fast blockchain-based verification system using Zero-Knowledge Proofs and Smart Contracts to enhance security and privacy in personal/user identification technology.
\item[--] Utilized the Dock blockchain to issue and manage decentralized identifiers and digital credentials, ensuring data integrity and mitigating possibilities for identity fraud.
\item[--] Reduced login waiting times by 17\% on average, compared to traditional two-factor authentication methods.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{STRENGTHS}
\begin{tabular}{@{} > {\bfseries}l @{\hspace{6ex}} l }
\vspace{0.35em}
Languages & Java, Python, C/C++, Kotlin, x64/x86 Assembly, R, LaTeX\\
\vspace{0.35em}
Frameworks & NumPy, Pandas, TensorFlow, Matplotlib, PyTorch, SciPy, JavaFX\\
\vspace{0.35em}
Technologies & Git, Linux/Unix, Blockchain, ROS/ROS2, Quantum Algorithms\\
\vspace{0.35em}
Soft Skills & Leadership, Critical Thinking, Communication, Problem Solving\\
\end{tabular}
\end{rSection}
\end{document}